%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvpublications}
%\vspace{-10.0mm}

%---------------------------------------------------------

\cvpublication
{(8) \textbf{Kovacs, N. A.}, Penev, P. I., Venapally, A., Petrov, A. S., Williams, L. D. ``Circular Permutation Obscures the Universality of a Ribosomal Protein", \textit{J. Mol. Evol.} 86, pgs 581-592 (2018)}
\vspace{-4.0mm}

%---------------------------------------------------------

\cvpublication
{(7) Bernier, C.R., Petrov, A. S., \textbf{Kovacs, N. A.},  Penev, P. I., Williams, L. D. ``Translation: The Universal Structural Core of Life", \textit{Mol. Biol. Evol.} 35, pgs 2065-2076 (2018)}
\vspace{-4.0mm}

%---------------------------------------------------------

\cvpublication
{(6) G{\'o}mez Ramos, L. M., Degtyareva, N. N., \textbf{Kovacs, N. A.}, Holguin, S. Y., Jiang, L., Petrov, A. S., Biesiada M., Hu, M. Y., Purzycka, K. J., Arya, D. P., Williams, L. D. ``Eukaryotic Ribosomal Expansion Segments as Antimicrobial Targets", \textit{Biochemistry} 56, pgs 5288-5299 (2017)}
\vspace{-4.0mm}

%---------------------------------------------------------

\cvpublication
{(5) \textbf{Kovacs, N.A.}, Petrov, A.S., Lanier, K.A., and Williams, L.D. ``Frozen in Time: The History of Proteins", \textit{Mol. Biol. Evol.} 34, pgs 1252-1260 (2017)}
\vspace{-4.0mm}

%---------------------------------------------------------

\cvpublication
{(4) G{\'o}mez Ramos, L.M., Smeekens, J.M., \textbf{Kovacs, N.A.}, Bowman, J.C., Wartell, R.M., Wu, R., and Williams, L.D. ``Yeast rRNA Expansion Segments: Folding and Function", \textit{J. Mol. Biol.} 428, pgs 4048-4059 (2016)}
\vspace{-4.0mm}

%---------------------------------------------------------

\cvpublication
{(3) Petrov, A.S., Gulen, B., Norris, A.M., \textbf{Kovacs, N.A.}, Bernier, C.R., Lanier, K.A., Fox, G.E., Harvey, S.C., Wartell, R.M., Hud, N.V., and Williams, L.D. ``History of the Ribosome and the Origin of Translation", \textit{Proc. Natl. Acad. Sci. U.S.A.} 112, pgs 15396-15401 (2015)}
\vspace{-4.0mm}

%---------------------------------------------------------

\cvpublication
{(2) Petrov, A.S., Bernier, C.R., Hsiao, C., Norris, A.M., \textbf{Kovacs, N.A.}, Waterbury, C.C., Stepanov, V.G., Harvey, S.C., Fox, G.E., Wartell, R.M., Hud, N.V., and Williams, L.D. ``Evolution of the Ribosome at Atomic Resolution", \textit{Proc. Natl. Acad. Sci. U.S.A.} 111, pgs 10251-10256 (2014)}
\vspace{-4.0mm}

%---------------------------------------------------------

\cvpublication
{(1) Sharma, M., Predeus, A.V., \textbf{Kovacs, N.A.}, and Feig, M. ``Differential Recognition Specificities of Eukaryotic MutS$\alpha$ and MutS$\beta$", \textit{Biophys. J.} 106, pgs 2483-2492 (2014)}
\vspace{-7.5mm}

%---------------------------------------------------------
\end{cvpublications}
