%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant} % Job title
    {Adviser: Dr. Loren Williams} % Organization
    {Georgia Institute of Technology} % Location
    {Aug 2013 - Current} % Date(s)
    {{\textbf{PhD Thesis}: \textit{The History of Proteins Revealed by Data Mining the Ribosome}}
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \vspace{4.0mm}
        \item {\textbf{Hypothesis}: The ribosome is a molecular fossil; its structure can be mined to unravel the evolution of life}
        \item {\textbf{Tools}: Python, PyMOL, Adobe Illustrator, Perl, MATLAB, JavaScript}
        \item {\textbf{Funding}: NASA Astrobiology Institute}
        \item {\textbf{Support}: Data analysis for experimental labmates}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {East Asia and Pacific Summer Institutes Fellow} % Job title
    {Adviser: Dr. Chiaolong Hsiao} % Organization
    {National Taiwan University} % Location
    {Jun 2017 - Aug 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {\textbf{Project}: The Evolution of Proteins in Eukaryotes: Data Mining the Ribosome Strucutre}
        \item {\textbf{Tools}: Python, PyMOL}
        \item {\textbf{Funding}: National Science Foundation - East Asia and Pacific Summer Institutes}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Undergraduate Research Associate} % Job title
    {Adviser: Dr. Michael Feig} % Organization
    {Michigan State University} % Location
    {Dec 2012 - May 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Project}: Molecular simulations of Mismatch Repair Enzymes MutS$\alpha$ and MutS$\beta$}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Molecular Biology Exchange Student} % Job title
    {Adviser: Dr. Peter Westhoff} % Organization
    {Heinrich-Heine Universit{\"a}t} % Location
    {May 2011 - Jul 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Project}: DNA-protein interaction of cis-regulatory elements in {\it Flaveria sp.}}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Undergraduate Research Associate} % Job title
    {Adviser: Dr. Yair Shachar-Hill} % Organization
    {Michigan State University} % Location
    {Jun 2010 - Mar 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Project}: Metabolic flux analysis of carbon through {\it Nanochloropsis sp.}}
        \item {\textbf{Project}: Aquaporin signalling in {\it Arabidopsis thaliana} gametogensis}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Research Associate} % Job title
    {Adviser: Dr. Cristoph Benning} % Organization
    {Michigan State University} % Location
    {Feb 2010 - May 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Project}: Protein-protein interactions in ER to chloroplast lipid trafficking}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\vspace{-4.0mm}
\end{cventries}
