%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Georgia Institute of Technology} % Job title
    {Graduate Research Assistant} % Organization
    {Atlanta, GA} % Location
    {Aug 2013 - Current} % Date(s)
    {{\textbf{Dissertation}: \textit{The Evolution of Proteins Revealed by Data Mining the Ribosome}}
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \vspace{4.0mm}
        \item {\textbf{Results}: Published 2 first-author papers and 5 coauthored papers. 3rd first-authored and 6th coauthored papers expected by graduation}
        \item {\textbf{Tools}: Python {\scriptsize(Numpy, Pandas, Scipy, SK-Learn, NetworkX, Biopython, PyMOL)}, Git, Perl, MATLAB, JavaScript, Bash, Adobe Illustrator}
%        \item {\textbf{Algorithms}: Linear Regression, SVM, Decision Trees, Random Forest, KNN, K-Means}
        \item {\textbf{Funding}: NASA, NSF - independently wrote grant to support summer research at National Taiwan University, including RT flights and housing}
        \item {\textbf{Collaboration}: Data analysis for experimental labmates}
        \item {\textbf{Communication}: Presented research as oral and poster presentations at 7 scientific conferences domestically and internationally}
        \item {\textbf{Mentoring}: Research mentor for undergraduate student. Awarded conference and travel funding} 
      \end{cvitems}
    }

 %---------------------------------------------------------
  \cventry
    {Project for CS 7280 - Network Science} % Job title
    {Atomic Interaction Network Analysis of the Ribosome} % Organization
    {Atlanta, GA} % Location
    {Fall 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {\textbf{Results}: Ribosomal RNA and protein folding domain prediction JuPyteR notebook}
        \item {\textbf{Tools}: Python {\tiny(Numpy, Pandas, Scipy, SK-Learn, NetworkX, Biopython, PyMOL)}}, Git
        \item {\textbf{Algorithms}: Louvain and Walktrap Community Dectection}
      \end{cvitems}
    }

 %---------------------------------------------------------
  \cventry
    {Project for BIOL 8803 - Programming for Bioinformatics and BIOL 7210 - Computational Genomics} % Job title
    {Analysis and Interpretation of \textit{Neisseria meningitidis} NGS Data} % Organization
    {Atlanta, GA} % Location
    {Fall 2014 and Spring 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {\textbf{Results}: Developed a genome browser of 53 annotated genomes and a typing tool that will identify a species from fasta file inputs}
        \item {\textbf{Tools}: Python, Perl, Git, \textit{de novo} Genome Assembly, SAMtools, BCFtools, GATK, Kent Source Tree, Bash, JBrowse, AWS}
      \end{cvitems}
    }

 %---------------------------------------------------------
  \cventry
    {Georgia Institute of Technology} % Job title
    {Graduate Teaching Assistant} % Organization
    {Atlanta, GA} % Location
    {9 Semesters} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Biophysical Chemistry Lab} - CHEM 4582 - 6 semesters - Instrucuted 8 undergraduate students per semester on experimental and computational biophysical chemistry protocols.}
        \item {\textbf{Macromolecular Structure} - CHEM 6572 - 2 semesters - Graded and instrucuted on the use of a computational modelling program for a class of approx. 25 graduate students.}
        \item {\textbf{Survey Biochemistry} - CHEM 3511 - 1 semester - Held weekly recitation for approx. 40 undergraduate students. Graded homework and exams.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Michigan State University; Heinrich-Heine Universit{\"a}t} % Job title
    {Undergraduate Research Assistant} % Organization
    {East Lansing, MI; D{\"u}sseldorf, DE} % Location
    {Feb 2010 - May 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Project}: Molecular simulations of Mismatch Repair Enzymes MutS$\alpha$ and MutS$\beta$. Coauthored paper}
        \begin{itemize}
        	\item {\textbf{Tools}: Bash, VMD, NAMD}
        \end{itemize}
        \item {\textbf{Project}: DNA-protein interaction of cis-regulatory elements in {\it Flaveria sp.}}
        \begin{itemize}
        	\item {\textbf{Tools}: Molecular clonging, yeast one- and two-hybrid screening, GUS staining, {\it A. thaliana, A. tumefaciens}}
        \end{itemize}
        \item {\textbf{Project}: Metabolic flux analysis of carbon}
        \begin{itemize}
        	\item {\textbf{Tools}: GC-MS, {\it Nanochloropsis sp.}}
        \end{itemize}
        \item {\textbf{Project}: Aquaporin signalling in gametogensis}
        \begin{itemize}
        	\item {\textbf{Tools}: PCR, {\it A. thaliana}}
        \end{itemize}
        \item {\textbf{Project}: Protein-protein interactions in ER to chloroplast lipid trafficking}
        \begin{itemize}
        	\item {\textbf{Tools}: Yeast two-hybrid screening, molecular cloning, {\it E. coli}}
        \end{itemize}
      \end{cvitems}
    }

%\vspace{-4.0mm}
%---------------------------------------------------------    
\vspace{-4.0mm}
\end{cventries}
