hspace{1em} My first 3 years of graduate school I served part-time as a teaching assistant which gave me excellent management experience as I instructed classes of 8 senior undergraduates on how to conduct bench-top biochemistry. I later wrote and was subsequently awarded scholarships to mentor an undergraduate in the 2017 Petit Undergraduate Research Scholars Program and to conduct research in Taiwan with the 2017 East Asia and Pacific Summer Institutes scholarship awarded by the NSF. My writing skills are further exemplified by my 8 published research articles which total over 160 citations, and my communications skills have been sharpened through poster and oral presentations at 7 conferences attended by scientists of disciplines ranging from ethics to astrophysics.

My research activities and projects related to my dissertation, coauthored papers, or class assignments have given me at least a sufficient foundation in all qualifications for this job while also making me a master of some all of the qualifications for this position in my PhD projects, research projects I collaborated and can effectively complete the duties and responsibilities of the job description. I have a PhD in boinformatics including 1 year of computational genomics experience as well as 5 years of structural bioinformatics experience. My computational genomics experience involved a course project where as a class, we developed a four-step pipeline was developed for the assembly, gene prediction, annotation, and comparative analysis of Next-Generation Sequencing data for fifty-three bacterial samples provided by the CDC, we then made our results available in an online genome browser as well as developed a tool to identify species and serotypes or serogroups of fasta inputs. In undergrad, I worked 10 hours a week for 5 semesters in molecular biology labs and also TAed for 7 semesters as a biochemistry teaching assistant. I coauthored 5 articles as a graduate student while publishing 2, soon to be , first-author publications. I have presented my research at 7 domestic and international conferences.



"Act like the person you needed when you were younger" is a mantra I hold closely, since I continuously strive to become a better version of myself and I like helping people realize their potential. Combining my desire to work on a multitude of assignments concerning the development of technology that directly improves the lives of people with my enjoyment of working on diverse projects while managing teams will make me a good TDLP fellow at BD. My intense curiosity, desire to help others, and belief in empowering others through problem-solving fits perfectly with what it means to become a leader within BD. I am available to begin work as early as January 2019 but can also work as a postdoc under my current advisor until summer 2019.