%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, letterpaper]{CV_latex_class}

% Configure page margins with geometry
\geometry{left=1.4cm, top=1.4cm, right=1.4cm, bottom=1.4cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo{./examples/profile.png}
\name{}{Nicholas Attila Kovacs}
\position{Bioinformaticist \& Data Scientist}
%\address{Dual US and Hungarian Citizen}

\mobile{(248) 895-2704}
\email{NAttilaKovacs@gmail.com}
%\citizenship{US Citizen}
\homepage{NicholasAKovacs.com}
\github{NicholasAKovacs}
\linkedin{NicholasAKovacs}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {ClearView Healthcare Partners}
  {275 Washington Street, Suite 405, Newton, MA 02458}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Application for Entry Level Consultant}
% How the letter is opened
\letteropening{Dear Ellis Greene and the ClearView Recruiting Team,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[See attached]{Resume}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  %{\today}
  {Nicholas Attila Kovacs~~~·~~~US Citizen}
  %{\thepage}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}

\hspace{1em} Transitioning from an experimental, bench-top biochemist to a computational biologist during the first year of my graduate career is a transition I am very proud of because I became the go-to guy in my lab and department to analyze data which led to my involvement in a diverse range of projects spanning molecular biology, chemistry, data science, big data, and computer science. Even though my PhD project asked perhaps the biggest and most fundamental question of biology or even science---how did life originate and evolve---, my curiosity is unbounded and collaborating on projects fed my desire to better understand the world around me. My transformation into a computational scientist also sparked my interest in entrepreneurship primarily via open-sourced software engineering which led me to enroll in the business course offered through my department titled "Concept-to-Market".

\hspace{1em} My first 3 years of graduate school I served part-time as a teaching assistant which gave me excellent management experience as I instructed classes of 8 senior undergraduates on how to conduct bench-top biochemistry. I later wrote and was subsequently awarded scholarships to mentor an undergraduate in the 2017 Petit Undergraduate Research Scholars Program and to conduct research in Taiwan with the 2017 East Asia and Pacific Summer Institutes scholarship awarded by the NSF. My writing skills are further exemplified by my soon to be 8 published research articles which total 144 citations, and my communications skills have been sharpened through poster and oral presentations at 7 academic conferences attended by scientists of disciplines ranging from ethics to astrophysics.

\lettersection{Why ClearView Healthcare Partners}

\hspace{1em} The breadth of the science, technology, and business problems faced by the bioscience companies ClearView works with provides a wide diversity of challenges that excite me as it will provide opportunities for personal growth and give me fullfillment by means of solving problems for companies whose products increase the quality of life for its customers. ClearView is regarded as an excellent place to work according to many different metrics. Reviews from employees of the company love their intelligent and ambitous coworkers, breadth of projects, meaningful work, and emphasis on mentorship. I am very open to moving to Boston, New York, or San Francisco.


\lettersection{Why Me?}

\hspace{1em} "Act like the person you needed when you were younger" is a mantra I hold closely, since I continuously strive to become a better version of myself and I like helping people realize their potential. Combining my desire for fast-paced projects and helping people succeed with my love of research, working in teams, and presenting will make me a good consultant. I am not at all burned out from graduate school; I have become accustomed to long working hours. My intense curiosity, desire to help others, and belief in empowering others through problem-solving fits perfectly with what it means to be a consultant at ClearView and I am available to begin work as early as January 2019 but can also work as a postdoc under my current advisor until summer 2019.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

%-------------------------------------------------------------------------------
\end{document}
